---
title: "OSM 2022 Analysis and Results WP"
author: "Pepijn Vink"
date: "`r Sys.Date()`"
output: html_document
---
```{r, include=FALSE}
knitr::opts_chunk$set(
  comment = "#>", echo = FALSE, fig.width = 6
)
```

# OSM 2022 Analysis and Results WP

```{r, message=FALSE}
# Load necessary packages
library(dplyr) # for data manipulation
library(ggplot2) # for visualization
library(magrittr) # for the pipe operator
library(tibble) # to create tibbles
library(foreign) # to import spss files
library(purrr) # for functional programming
library(skimr) # for descriptives
library(knitr)
library(rlang)
```

```{r}
# Load necessary functions
## for descriptives
source("osm_descriptives.R")

## for attitude behavior gap
source("att_beh_gap.R")

# load variable names to use
load("variables_WP.RData")
```


## Reading In the data

First specify the file path.

```{r, echo = T}
# filtered dataset
file <- "~/surfdrive/Shared/OS Monitor 2022/Data/Data/UOS WP_ Open Science Monitor 2022.sav"
data_full<- read.spss(file, to.data.frame = TRUE) # read in the data
```

We will only analyze those that gave consent, have not retired yet, and are part of scientific staff. In addition, we will only assess respondents that have a maximum of 50% (6) missings on questions on awareness. First, we will compute a variable that represents this, and then we will filter out respondents. We assign this to a new object 'dat' which we will perform our analyses on.

```{r}
# select columns to use
data_raw <- data_full[, vars_WP]
# filter out people
dat_withoutID <- data_raw %>%
  filter(Data_consent == 1,
         pens == "niet gepensioneerd",
         wp == "wp") %>%
  mutate(missing_awareness = apply(.[,22:33], 1, function(x) x %>% is.na() %>% sum())) %>% # compute number of missings
  filter(missing_awareness <= 6) %>% # filter out persons with >6 missings
  select(-missing_awareness) # remove missingness variable

# create ID column
ID <- 1:nrow(dat_withoutID)
dat <- cbind(ID, dat_withoutID)
```

## Get some basic descriptives

```{r}
# create descriptives for some variables
map(dat[,c("Faculty_2", "Pos_2", "OSCU", "Gen", "Nationality")], 
    table)
```
## Descriptives of Awareness {.tabset}

The code below prints the frequencies of awareness as tabs.

```{r, results='asis'}
# create list with tables
descr_aw <- dat[,23:34] %>%
  map(table)

# format tables
osm_descriptives(descr_aw, '###')
```

## Descriptives of Awareness by Position {.tabset}

### PhD {.tabset}

```{r, results='asis'}
descr_aw<- dat[dat$Pos_2 == 'PhD candidate', 23:34] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_aw, '####')
```

### Post-doc {.tabset}

```{r, results='asis'}
descr_aw<- dat[dat$Pos_2 == 'Post-doc', 23:34] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_aw, '####')
```

### Junior Teacher {.tabset}

```{r, results='asis'}
descr_aw<- dat[dat$Pos_2 == '(Junior) teacher', 23:34] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_aw, '####')
```

### Assistant Professor {.tabset}

```{r, results='asis'}
descr_aw<- dat[dat$Pos_2 == 'Assistant professor', 23:34] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_aw, '####')
```

### Associate Professor {.tabset}

```{r, results='asis'}
descr_aw<- dat[dat$Pos_2 == 'Associate professor', 23:34] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_aw, '####')
```

### Full Professor {.tabset}

```{r, results='asis'}
descr_aw<- dat[dat$Pos_2 == 'Full professor', 23:34] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_aw, '####')
```

## Descriptives of Attitudes {.tabset}

The code below prints the frequencies of attitudes as tabs.

```{r, results='asis'}
# create list with tables
descr_att <- dat[,35:46] %>%
  map(table)

# format tables
osm_descriptives(descr_att, '###')
```

## Descriptives of Attitudes by Position {.tabset}

### PhD {.tabset}

```{r, results='asis'}
descr_att<- dat[dat$Pos_2 == 'PhD candidate', 35:46] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_att, '####')
```

### Post-doc {.tabset}

```{r, results='asis'}
descr_att<- dat[dat$Pos_2 == 'Post-doc', 35:46] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_att, '####')
```

### Junior Teacher {.tabset}

```{r, results='asis'}
descr_att<- dat[dat$Pos_2 == '(Junior) teacher', 35:46] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_att, '####')
```

### Assistant Professor {.tabset}

```{r, results='asis'}
descr_att<- dat[dat$Pos_2 == 'Assistant professor', 35:46] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_att, '####')
```

### Associate Professor {.tabset}

```{r, results='asis'}
descr_att<- dat[dat$Pos_2 == 'Associate professor', 35:46] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_att, '####')
```

### Full Professor {.tabset}

```{r, results='asis'}
descr_att<- dat[dat$Pos_2 == 'Full professor', 35:46] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_aw, '####')
```

## Descriptives of Behaviors {.tabset}

The code below prints the frequencies of behaviors as tabs.

```{r, results='asis'}
# create list with tables
descr_beh <- dat[,47:58] %>%
  map(table) %>%
  map(as.data.frame)

# format tables
osm_descriptives(descr_beh, '###')
```

## Descriptives of Behaviors by Position {.tabset}

### PhD {.tabset}

```{r, results='asis'}
descr_beh<- dat[dat$Pos_2 == 'PhD candidate', 47:58] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_beh, '####')
```

### Post-doc {.tabset}

```{r, results='asis'}
descr_beh<- dat[dat$Pos_2 == 'Post-doc', 47:58] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_beh, '####')
```

### Junior Teacher {.tabset}

```{r, results='asis'}
descr_beh<- dat[dat$Pos_2 == '(Junior) teacher', 47:58] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_beh, '####')
```

### Assistant Professor {.tabset}

```{r, results='asis'}
descr_beh<- dat[dat$Pos_2 == 'Assistant professor', 47:58] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_beh, '####')
```

### Associate Professor {.tabset}

```{r, results='asis'}
descr_beh<- dat[dat$Pos_2 == 'Associate professor', 47:58] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_beh, '####')
```

### Full Professor {.tabset}

```{r, results='asis'}
descr_beh<- dat[dat$Pos_2 == 'Full professor', 47:58] %>%
  map(table) %>%
  map(as.data.frame)

osm_descriptives(descr_beh, '####')
```

## Attitude-Behavior Gap

### Full sample

```{r, warning = F}
att_beh_gap_full <- att_beh_gap(data = dat)
kable(att_beh_gap_full, digits = 3)
```

### Attitude Behavior Gap by Position {.tabset}

```{r, echo=F}
positions <- c("PhD candidate", "Post-doc", "(Junior) teacher", "Assistant professor", "Associate professor", "Full professor")
```

```{r, warning=FALSE}
att_beh_positions <- vector(mode = "list", length = 6)
for(i in seq_along(positions)){
  pos <- positions[i]
  att_beh_positions[[i]] <- att_beh_gap(position = pos, data = dat)
}
names(att_beh_positions) <- positions
```

```{r, results = 'asis'}
for (i in seq_along(att_beh_positions)){
    cat('####', names(att_beh_positions)[i], "\n")
    cat("\n")
    print(kable(att_beh_positions[[i]], caption = cat("Attitude behavior gap Analysis for ", names(att_beh_positions)[i], "\n"), digits = 3))
    cat("\n")
  }
```

### Attitude Behavior Gap by Faculty {.tabset}

```{r, echo=F}
faculties <- levels(dat$Faculty_2)[1:7]
```

```{r, warning=FALSE}
att_beh_faculties <- vector(mode = "list", length = 7)
for(i in seq_along(faculties)){
  fac <- faculties[i]
  att_beh_faculties[[i]] <- att_beh_gap(faculty = fac, data = dat)
}
names(att_beh_faculties) <- faculties
```

```{r, results = 'asis'}
for (i in seq_along(att_beh_faculties)){
    cat('####', names(att_beh_faculties)[i], "\n")
    cat("\n")
    print(kable(att_beh_faculties[[i]], caption = cat("Attitude behavior gap analysis for ", names(att_beh_faculties)[i], "\n"), digits = 3))
    cat("\n")
  }
```

## Opportunities {.tabset}

```{r}
# copy data frame to use
dat_opp <- dat %>%
  mutate_at(
    vars(dplyr::starts_with("OppMat")), as.numeric
  ) %>%
  mutate_at(
    vars(dplyr::starts_with("OppMat")),
    ~case_when(
      . == 1 | . == 2 ~ 1,
      . == 3 ~ 2,
      . == 4 | . == 5 ~ 3,
      is.na(NA) ~ NA
    )) %>%
  select(dplyr::starts_with("OppMat"))

opportunities <- dat_opp %>%
  map_df(table) %>%
  mutate(n = rowSums(.),
         missing = nrow(dat)-n)

colnames(opportunities) <- c("(Strongly) disagree", "Neutral", "(Strongly) Agree", "n", "missing")

opportunities <- as.data.frame(opportunities)

opp_rownames <- c("...improve quality of scientific knowledge",
         "...detect unethical behavior in research practices",
         "...improve diversity and inclusion in academia",
         "...improve fairness in reward and promotion systems in academia",
         "...create more career opportunities for young academics",
         "...increase the societal impact of scientific work",
         "...increase inter- or multidisciplinary collaborations between academics",
         "...improve collaborative atmosphere among collegues",
         "...improve the quality of education",
         "...learn from each others’ mistakes and talk openly about them")

rownames(opportunities) <- opp_rownames

opportunities_perc <- opportunities %>%
  mutate_at(1:3, ~ ./n*100)
```

### Raw Values

```{r}
kable(opportunities, digits = 2)
```

### Percentages

```{r}
kable(opportunities_perc, digits = 2)
```

## Barriers {.tabset}

```{r}
# copy data frame to use
dat_bar <- dat %>%
  mutate_at(
    vars(dplyr::starts_with("BarMat")), as.numeric
  ) %>%
  mutate_at(
    vars(dplyr::starts_with("BarMat")),
    ~case_when(
      . == 1 | . == 2 ~ 1,
      . == 3 ~ 2,
      . == 4 | . == 5 ~ 3,
      is.na(NA) ~ NA
    )) %>%
  select(dplyr::starts_with("BarMat"))

barriers <- dat_bar %>%
  map_df(table) %>%
  mutate(n = rowSums(.),
         missing = nrow(dat)-n)

colnames(barriers) <- c("(Strongly) disagree", "Neutral", "(Strongly) Agree", "n", "missing")

barriers <- as.data.frame(barriers)

bar_rownames <- c("...my workload is too high to integrate these practices",
                  "...I do not get time within my contract hours to do / learn this",
                  "...I do not get recognition from my supervisor for this",
                  "...it is not the norm to do this in my department (my colleagues don’t do it)",
                  "...there is insufficient practical support and training available in my department about this",
                  "...I would lose autonomy and freedom in how I do my work research",
                  "...my research does not allow for it due to for example the GDPR, embargos and or patent issues",
                  "...many OS practices do not fit with the culture of competition that exists in my department",
                  "...career promotion and success still heavily rely on “individual excellence” standards that do not fit with many OS practices",
                  "...I am afraid that if I make a mistake in my OS practices, it will be held against me (e.g., by being publicly shamed, orseen as fraudulent)")

rownames(barriers) <- bar_rownames

barriers_perc <- barriers %>%
  mutate_at(1:3, ~ ./n*100)
```

### Raw Values

```{r}
kable(barriers, digits = 2)
```

### Percentages

```{r}
kable(barriers_perc, digits = 2)
```


